### 2023-06-12 README.Rmd
nfbfhsodfjjhr

---
output: github_document
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

@@

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
and can also predict outside task that were not included in estimating
your utility scores. Although commercial studies often do not include a
validation/holdout task [@yang2018], it is highly recommended to do so
[@Orme.2015; @rao2014a]. This validation/ holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study these have to be programmed by yourself.

👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data,
and running your initial Hierarchical Bayes models, you can turn to
<code>validateHOT</code> and test how good your model predicts choices
in the validation/ holdout task. Herefore, you only have to insert your
raw utility scores as well as the actual choice of your validation/
holdout task. You can use the <code>merge()</code> provided by
<code>base</code> package [@base]. Afterward, you can read in your data
file and enjoy <code>validateHOT</code>.

@@

For all 3 key areas, the <code>createHOT</code> function is essential.
This function creates the total utilities for each alternative in the
validation/holdout task and also in the simulation method, respectively.
@rao2014a [p. 82] mentions the additive utility model stating that the
total utility of a profile or conjoint model is the sum of its attribute
levels. <code>createHOT</code> will do exactly this for you.

@@

<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
divergence between the actual choice distribution and the predicted
choice distribution [@ding2011; @philentropy]. Output provides both
divergence between predicted from observed and observed from predicted
due to the asymmetry of the Kullback-Leibler divergence. If you specify
an optional <code>Group</code> argument the output is split by
groups.</li>

@@

We also include metrics from machine learning, i.e., the confusion
matrix (e.g., @Burger2018). For all of the 5 provided functions, you
currently have to have a **none** option in your data. We currently
predict, e.g., whether a buy or no-buy was correctly predicted.
Information could be used for overestimating and underestimating,
respectively, of product purchases. In the following <code>TP</code>
stands for true positives, <code>FP</code> for false positives,
<code>TN</code> for true negatives, and <code>FN</code> for false
negatives.

@@

<li><code>f1</code>: defined as
$\frac{2 * precision * recall}{precision + recall}$ or stated
differently by Burger [-@Burger2018] $\frac{2TP}{2TP + FP + FN}$. If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

@@

<li><code>freqassort</code>: Inspired by the former
[turfR](https://github.com/cran/turfR) package, <code>freqassort</code>
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment.
For the <code>method</code> argument you can decide between <code>method
= "threshold"</code> (if utility of product is larger than the utility
of <code>None</code>, it is marked as potential purchase option) and
<code>method = "First Choice"</code> (only product with highest utility
is considered. If its utility is above the utility of <code>None</code>,
it is marked as potential purchase option). If you specify an optional
<code>Group</code> argument the output is split by groups.</li>

<li><code>reach</code>: Inspired by the former
[turfR](https://github.com/cran/turfR) package, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(buy at least one of the products) with your in the function determined
potential assortment. or the <code>method</code> argument you can decide
between <code>method = "threshold"</code> (if utility of product is
larger than the utility of <code>None</code>, it is marked as potential
purchase option) and <code>method = "First Choice"</code> (only product
with highest utility is considered. If its utility is above the utility
of <code>None</code>, it is marked as potential purchase option). If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

@@

We are teaching a preference measurement seminar for students. Often
these students did not have experience with *R* before or only sparsely.
We teach them to also validate their results and wanted to give them an
easy way on how to do this in *R*. Of course, there are other great
packages which are even faster in running (i.e., @Metrics), however,
these packages need some more data wrangling in order to use the
appropriate functions, which might be a burden or barrier for the one or
the other.

Moreover, as @yang2018 also report, often commercial studies do not use
any validation task. Some market research companies (as far as we have
realized) are not that familiar with *R* yet. Since these functions are
not always implemented in other softwares, this might be one reason why
they do not include one simply because they do not know how to use it
correctly. Having a package to evaluate the validation/ holdout task can
also be beneficial for those companies.

@@

> &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this. However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package [@base]. For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.

@@

In this case, the Grouping variable is just an integer. However, the output is different if it is a factor or if it is labelled data. To proof this we just quickly change <code>Group</code> in a factor by using the <code>factor()</code> function provided by @base.

@@

>>>>

---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

@@

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
and can also predict outside task that were not included in estimating
your utility scores. Although commercial studies often do not include a
validation/holdout task (Yang et al., 2018), it is highly recommended to do so
(Orme, 2015; Rao, 2014). This validation/ holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study these have to be programmed by yourself.

👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data,
and running your initial Hierarchical Bayes models, you can turn to
<code>validateHOT</code> and test how good your model predicts choices
in the validation/ holdout task. Herefore, you only have to insert your
raw utility scores as well as the actual choice of your validation/
holdout task. You can use the <code>merge()</code> provided by
<code>base</code> package (R Core Team, 2023). Afterward, you can read in your data
file and enjoy <code>validateHOT</code>.

@@

For all 3 key areas, the <code>createHOT</code> function is essential.
This function creates the total utilities for each alternative in the
validation/holdout task and also in the simulation method, respectively.
Rao (2014, p. 82) mentions the additive utility model stating that the
total utility of a profile or conjoint model is the sum of its attribute
levels. <code>createHOT</code> will do exactly this for you.

@@

<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
divergence between the actual choice distribution and the predicted
choice distribution (Ding et al., 2011; Drost, 2018). Output provides both
divergence between predicted from observed and observed from predicted
due to the asymmetry of the Kullback-Leibler divergence. If you specify
an optional <code>Group</code> argument the output is split by
groups.</li>

@@

We also include metrics from machine learning, i.e., the confusion
matrix (e.g., Burger, 2018). For all of the 5 provided functions, you
currently have to have a **none** option in your data. We currently
predict, e.g., whether a buy or no-buy was correctly predicted.
Information could be used for overestimating and underestimating,
respectively, of product purchases. In the following <code>TP</code>
stands for true positives, <code>FP</code> for false positives,
<code>TN</code> for true negatives, and <code>FN</code> for false
negatives.

@@

<li><code>f1</code>: defined as
$\frac{2 * precision * recall}{precision + recall}$ or stated
differently by Burger (2018) $\frac{2TP}{2TP + FP + FN}$. If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

@@

<li><code>freqassort</code>: Inspired by the former <a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>freqassort</code>
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment.
For the <code>method</code> argument you can decide between <code>method
= "threshold"</code> (if utility of product is larger than the utility
of <code>None</code>, it is marked as potential purchase option) and
<code>method = "First Choice"</code> (only product with highest utility
is considered. If its utility is above the utility of <code>None</code>,
it is marked as potential purchase option). If you specify an optional
<code>Group</code> argument the output is split by groups.</li>

<li><code>reach</code>: Inspired by the former
<a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(buy at least one of the products) with your in the function determined
potential assortment. or the <code>method</code> argument you can decide
between <code>method = "threshold"</code> (if utility of product is
larger than the utility of <code>None</code>, it is marked as potential
purchase option) and <code>method = "First Choice"</code> (only product
with highest utility is considered. If its utility is above the utility
of <code>None</code>, it is marked as potential purchase option). If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

@@

We are teaching a preference measurement seminar for students. Often
these students did not have experience with *R* before or only sparsely.
We teach them to also validate their results and wanted to give them an
easy way on how to do this in *R*. Of course, there are other great
packages which are even faster in running (i.e., Hamner & Frasco, 2018), however,
these packages need some more data wrangling in order to use the
appropriate functions, which might be a burden or barrier for the one or
the other.

Moreover, as Yang et al. (2018) also report, often commercial studies do not use
any validation task. Some market research companies (as far as we have
realized) are not that familiar with *R* yet. Since these functions are
not always implemented in other softwares, this might be one reason why
they do not include one simply because they do not know how to use it
correctly. Having a package to evaluate the validation/ holdout task can
also be beneficial for those companies.

@@

> &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this. However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package (R Core Team, 2023). For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.

@@

In this case, the Grouping variable is just an integer. However, the output is different if it is a factor or if it is labelled data. To proof this we just quickly change <code>Group</code> in a factor by using the <code>factor()</code> function provided by R Core Team (2023).

@@

Burger, Scott V. 2018. <em>Introduction to Machine Learning with R: Rigorous Mathematical Analysis</em>. O'Reilly.

Ding, Min, John R. Hauser, Songting Dong, Daria Dzyabura, Zhilin Yang, SU Chenting, and Steven P. Gaskin. 2011. “Unstructured Direct Elicitation of Decision Rules.” <em>Journal of Marketing Research 48</em>(1): 116-27. [https://doi.org/10.1509/jmkr.48.1.116](https://doi.org/10.1509/jmkr.48.1.116)

Drost, Hajk-Georg. 2018. “Philentropy: Information Theory and Distance Quantification with R” <em>Journal of Open Source Software 3</em>(26), 765, [https://joss.theoj.org/papers/10.21105/joss.00765](https://joss.theoj.org/papers/10.21105/joss.00765).

Hamner, Ben, and Michael Frasco. 2018. “Metrics: Evaluation Metrics for Machine Learning.” [https://CRAN.R-project.org/package=Metrics](https://CRAN.R-project.org/package=Metrics).

Orme, Bryan K. 2015. “Including Holdout Choice Tasks in Conjoint Studies.” [https://sawtoothsoftware.com/resources/technical-papers/including-holdout-choice-tasks-in-conjoint-studies](https://sawtoothsoftware.com/resources/technical-papers/including-holdout-choice-tasks-in-conjoint-studies).

R Core Team. 2023. “R: A Language and Environment for Statistical Computing.” [https://www.R-project.org/](https://www.R-project.org/).

Rao, Vithala R. 2014. <em>Applied Conjoint Analysis.</em> Springer Berlin Heidelberg. [https://doi.org/10.1007/978-3-540-87753-0](https://doi.org/10.1007/978-3-540-87753-0).

Yang, Liu (Cathy), Olivier Toubia, and Martijn G. de Jong. 2018. “Attention, Information Processing, and Choice in Incentive-Aligned Choice Experiments.” <em>Journal of Marketing Research 55</em>(6): 783–800. [https://doi.org/10.1177/0022243718817004](https://doi.org/10.1177/0022243718817004).
